---
title: "Fitting a Multiple Linear Regression Model"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidymodels)
library(GGally)
```

```{r reading the dataset}
hfi <- read_csv("https://www.openintro.org/data/csv/hfi.csv")
```

Plottig a density graph to display the distribution of pfi_score

```{r}
ggplot(hfi, aes(x = pf_score)) +
  geom_density()
```

The density graph is negatively skewed. It also has 3 peak. The distribution appears to be biomodal with the main peak around 6.5 and another significant peak around 8.9. 

## Pairwise Relationships

```{r, warning=FALSE}
hfi %>%
  select(ends_with("_score")) %>%
  ggpairs()
```

From this visualization, all variables have linear patterns. Pf_score has a bimodal distribution with 3 peaks and is negatively skewed, ef_score is negatively skewed and appears to have a normal distribution, while hf_score has a bimodal distribution which is also negatively skewed.

## The Multiple Linear Regression Model

```{r}
m_hr_ef <- lm(pf_score ~ hf_score + ef_score, data = hfi)
tidy(m_hr_ef)
```

The estimated equation is y = 1.46 + 2.00(hf_score) - 1.00(ef_score).

For countries with ef_score and hf_score of 0, we expect their mean pf_score to be 1.46. 

For every 1 unit increase in ef_score we expect the pf_score to decrease by 1 unit.

For every 1 unit increase in hf_score we expect the pf_score to increse by 2 units.

##3D Plots

```{r, warning=FALSE}
library(plotly)

plot1 <- plot_ly(
  hfi, x = ~hf_score , y = ~ef_score, z = ~pf_score, sizes = c(0.5,0.5,0.5)
)

```


```{r}
# review any visual patterns
hfi %>%
  select(pf_score, pf_expression_influence, pf_expression_control) %>%
  ggpairs()

# fit the mlr model
m_pf <- lm(pf_score ~ pf_expression_influence + pf_expression_control, data = hfi)
tidy(m_pf)
```

For countries with a pf_expression_influence of 0 (those with the largest amount of laws/regulations on media content) and pf_expression_control of 0 (those with the largest amount of political pressure on media content), we expect their mean personal freedom score to be 4.71.

For a given pf_expression_control value (i.e., a given level of laws/regulations on media content), a 1 unit increase in pf_expression_influence is associated with a 0.188 unit increase of a country’s mean personal freedom score.

For a given pf_expression_influence value (i.e., a given level of political pressure on media content), a 1 unit increase in pf_expression_control is associated with a 0.288 unit increase of a country’s mean personal freedom score.

# Relationship between the response and predictors
```{r}
summary(m_pf)
```

F-statistic:  1308 on 2 and 1375 DF,  p-value: < 2.2e-16
Reject null hypotheses

```{r}
glance(m_pf)
```

To check for linearlity Assumption
```{r}
# obtain fitted values and residuals
m_pf_aug <- augment(m_pf)

# plot fitted values and residuals
ggplot(data = m_pf_aug, aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
  xlab("Fitted values") +
  ylab("Residuals")
```

Checking for Normality assumption
```{r}
ggplot(data = m_pf_aug, aes(x = .resid)) +
  geom_histogram(binwidth = 0.25) +
  xlab("Residuals")
```

# Predictiom

```{r}
hfi %>% 
  filter(countries == "United States" & year == 2016) %>% 
  select(pf_score, pf_expression_influence, pf_expression_control)
```


```{r}
hfi %>% 
  filter(countries == "United States" & year == 2016) %>% 
  predict(m_pf, .)
```

